---
title: "Carp Network Topology"
author: "Lauren White"
date: "2/26/2020"
output: html_document
---

Script to focus on daily network properties/topology at Boat Ramp site.

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stringr)
library(lubridate)
library(Matrix)
library(igraph)
library(bipartite)
library(data.table)
library(ggplot2)
library(gganimate)
```

## Boatramp
### Load PIT Tag capture and Boatramp site-specific data

```{r, echo=FALSE}
#Capture data: refromat capture date as POISXct; retain PIT#, species, and capture date
pit_capture <-read.csv("test_2019_01_21.csv", stringsAsFactors = FALSE, colClasses = "character")
pit_capture<- select(pit_capture, c(Lake, PIT, Length, Sex))
pit_capture$PIT<-as.character(pit_capture$PIT)
head(pit_capture)
length(unique(pit_capture$PIT))

#Boat Ramp Site  

boatramp<-read.table("Boat_ramp_complete.log", header=FALSE, fill=TRUE,col.names=c("D", "Date", "Time", "Time2", "HA", "PIT", "Antenna", "Col1","Col2"), na.strings=c("", "NA"))
boatramp<-select(boatramp, c(Date, Time, PIT, Antenna))

boatramp$DATETIME<- as.POSIXct(paste(boatramp$Date,boatramp$Time), format='%Y-%m-%d %H:%M:%S', tz="CDT") #Reformat as POSIXct
boatramp<-boatramp[-which(is.na(boatramp$DATETIME)),] #remove NA values
boatramp$PIT<-as.character(boatramp$PIT) #toString(boatramp$PIT)
boatramp$PIT<-str_sub(boatramp$PIT, 11, 16)
boatramp$PIT[boatramp$PIT==""] <- NA
boatramp<-boatramp[-which(is.na(boatramp$PIT)),]
boatramp<-boatramp[-which(boatramp$PIT=="390146"),] #This PIT ID has a 2018 read (prior to data collection start)
boatramp$Site<-"B"
# write.csv( boatramp, "cleaned_boatramp.csv")

merged_br<- merge(boatramp, pit_capture,  by="PIT")
# merged_br<-boatramp
head(merged_br)

length(unique(merged_br$PIT))
```

### Are there any "super feeders"?
How many days out of the total number of sampling days did fish visit any of the antenna at Boat Ramp?

```{r}
dates<-unique(merged_br$DATETIME) #how many dates of observation in dataset?
(min_date<-min(dates))
(max_date<-max(dates))

start_date<-as.POSIXct("2019-07-23 12:00:00 CDT")
end_date<-as.POSIXct("2019-10-29 12:00:00 CDT")
num_days<-as.numeric(end_date-start_date)

superfish<-data.frame(fishID=unique(merged_br$PIT), nvisit=rep(NA,length(unique(merged_br$PIT)))) 

for (i in 1:length(unique(merged_br$PIT))){
    fishID<-unique(merged_br$PIT)[i]
    visit_count<-0
    for (j in 1:num_days){
        sub_combined<-merged_br %>% filter(DATETIME >= as.POSIXct(start_date+ (j-1)*86400, tz="CDT") & DATETIME <= as.POSIXct(start_date + j*86400, tz="CDT")) #86400 seconds/24 hours
        fishID %in% sub_combined$PIT
    if(fishID %in% sub_combined$PIT){
      visit_count<-visit_count+1
    }
    }
    superfish$nvisit[i]<-visit_count
}

hist(superfish$nvisit, xlab="Number of sampling days", main="")
```


### Daily network topology and feeder visiting behavior

```{r}

network_df <-data.frame(day=1:num_days, nnodes=rep(NA,num_days), mean_degree=rep(NA, num_days), transitivity=rep(NA, num_days), edge_density=rep(NA, num_days), diameter=rep(NA, num_days), centralization=rep(NA, num_days), eigen= rep(NA, num_days), btwn= rep(NA, num_days),modularity=rep(NA, num_days))
degree_list<-NULL

for(i in 1:num_days){
  sub_combined<-merged_br %>% filter(DATETIME >= as.POSIXct(start_date+ (i-1)*86400, tz="CDT") & DATETIME <= as.POSIXct(start_date + i*86400, tz="CDT")) #86400 seconds/24 hours
  # print(sub_combined)
  

  
  edgelist<-data.frame(PIT=sub_combined$PIT, Reader=sub_combined$Antenna)
  network_df$nnodes[i]<-length(unique(sub_combined$PIT))
  
if(nrow(edgelist)>0){
  A <- spMatrix(nrow=length(unique(edgelist$PIT)),
          ncol=length(unique(edgelist$Reader)),
          i = as.numeric(factor(edgelist$PIT)),
          j = as.numeric(factor(edgelist$Reader)),
          x = rep(1, length(as.numeric(edgelist$PIT))) )
  row.names(A) <- levels(factor(edgelist$PIT))
  colnames(A) <- levels(factor(edgelist$Reader))
  
  bi<-graph.incidence(A, mode="all") #undirected, named graph that is bipartite
  pr<-bipartite.projection(bi) 
  #co-membership network of nodes ($proj1), or a network of groups that share members ($proj2)
  plot(pr$proj1, main=paste("Day =", i))
  g<- ggplot(data=sub_combined, aes(DATETIME, as.factor(PIT), color=Antenna)) +
  geom_point(alpha=0.5)
  print(g)
  
  network_df$mean_degree[i]<-mean(degree_distribution(pr$proj1))
  network_df$transitivity[i]<-transitivity(pr$proj1, "global")
  network_df$edge_density[i]<-edge_density(pr$proj1, loops=F)
  network_df$diameter[i]<-diameter(pr$proj1, directed=F, weights=NA)
  network_df$centralization[i]<-centr_degree(pr$proj1, loops=FALSE, normalized=T)$centralization
  network_df$eigen[i]<-centr_eigen(pr$proj1, directed=F, normalized=T)$centralization 
  network_df$btwn[i]<-centr_betw(pr$proj1, directed=F, normalized=T)$centralization
  network_df$modularity[i]<-modularity(pr$proj1, membership(cluster_walktrap(pr$proj1)))
  }
}

head(network_df)
```

Look at changes in network topology through time
```{r}
plot(network_df$day, network_df$nnodes, type="l", xlab= "Sampling day", ylab="Number of nodes in daily network")
points(network_df$day, network_df$nnodes, col="red")

plot(network_df$day, network_df$edge_density, type="l", xlab= "Sampling day", ylab="Edge density")
points(network_df$day, network_df$edge_density, col="blue")

plot(network_df$day, network_df$transitivity, type="l", xlab= "Sampling day", ylab="Global transitivity")
points(network_df$day, network_df$transitivity, col="blue")

plot(network_df$day, network_df$diameter, type="l", xlab= "Sampling day", ylab="Network diameter")
points(network_df$day, network_df$diameter, col="blue")

plot(network_df$day, network_df$centralization, type="l", xlab= "Sampling day", ylab="Normalized centralization")
points(network_df$day, network_df$centralization, col="blue")


plot(network_df$day, network_df$modularity, type="l", xlab= "Sampling day", ylab="Modularity")
points(network_df$day, network_df$modularity, col="blue")


plot(network_df$day, network_df$eigen, type="l", xlab= "Sampling day", ylab="Eigenvalue centralization")
points(network_df$day, network_df$eigen, col="blue")


plot(network_df$day, network_df$btwn, type="l", xlab= "Sampling day", ylab="Betweenness centralization")
points(network_df$day, network_df$btwn, col="blue")




```


### Time between visits
```{r}
A1<-merged_br %>% filter(Antenna == "A1") 
A2<-merged_br %>% filter(Antenna == "A2")
A3<-merged_br %>% filter(Antenna == "A2") 

length(unique(A1$PIT))
length(unique(A2$PIT))
length(unique(A3$PIT))
```



### Next steps:
- Lagged association rates (LAR)- Whitehead, H. (1995) Investigating structure and temporal scale in social organizations using identified individuals. Behavioral Ecology, 6, 199– 208.
- `asnipe` package
- Damien Farine's work in finches?
- Ben Sheldon's work on great tits?
